Title

### 2023-09-19 main.tex
2qbits

@@

\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
We can see that just as in \fref{Fig3}, fidelities are high for points close to the depolarizing channel 
($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{FigS2q} 
\end{figure} % }}}

>>>>

{\color{green}
\subsection{Two-qubit Pauli channels}
\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two principal
qubits and $2N$ ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the number of ancilla qubits can be reduced for Pauli 
channels in which not all two-qubit Pauli matrices are applied to
the system. For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  (\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  (\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}a).

\begin{figure} % {{{
\centering
\includegraphics{images/qbit-im.pdf}
\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two ancilla qubits can be constructed just as it was done for \fref{Fig2}. }
\label{2qbit}
\end{figure} % }}}

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
matrix by doing quantum process tomography on
the two principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}b).

}

@@

{\color{green}
\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
We can see that just as in \fref{Fig3}, fidelities are high for points close to the depolarizing channel 
($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{fid} 
\end{figure} % }}}
}
